Automated verification of stand-alone solar photovoltaic systems

### 2018-11-18 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
added additional comments
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

However, there is a main disadvantage of model checking: the state explosion problem. In order to solve this problem, many different techniques were developed at the last decades. One of the first major advances was symbolic model checking with binary decision diagrams (BDDs). In this approach, a set of states is represented by a BDD instead of by listing each state individually, which is often exponentially smaller in practice. Another major advance is the partial order reduction, which exploits the independence of actions in a system with asynchronous composition of processes. A third major advance is counterexample-guided abstraction refinement, which adaptively tries to find an appropriate level refinement, not burdened with irrelevant detail that slows down verification \cite{Clarke2012}. However, one of the most promising approaches is Bounded Model Checking (BMC).

BMC is a method that checks the model up to a given path in the path length. BMC algorithms traverses a finite state machine for a fixed number of steps, $ k $, and checks whether violation occurs with this bound. It uses Boolean Satisfiability (SAT) solvers, where SAT means satisfiability. SAT problem is a problem of determining if there are certain conditions or interpretations that satisfy a given Boolean expression \cite{ClarkeHV18}. %SAT solvers are used in BMC, such that i
%If there are some Boolean function, t
The SAT solver would search the model for conditions (value of variables) that would make the formula $TRUE$. If a SAT solver finds a substitution for the formula/function then the substitute induces a counterexample.  
%
%CBMC is considering the best-known model verification tool to validate code in ANSI-C and C++ \cite{Kroening}. 
%
%\textcolor{red}{ESBMC does not use CBMC as its main frontend. Please take a look at this paper and cite it: https://ssvlab.github.io/lucasccordeiro/papers/ase2018.pdf. I would also suggest to remove the above sentence.}
%
ESBMC is one of the most representatives context-bounded model checkers for embedded C/C++ software based on Satisfiability Modulo Theories (SMT) solver~\cite{esbmc2018}. %, which can use CBMC as front-end.
%The use of SMT, instead of Boolean Satisfiability SAT from the original BMC, 
ESBMC comes as an alternative to overcome limitations of the systems modeling, especially considering that the complexity of these is increasing and the SMT method has high level and richer theories than the SAT to represent the models.

\subsection{ESBMC }
ESBMC (or Efficient SMT-based Bounded Model Checker) is an open source, permissively licensed (Apache 2), cross platform bounded model checking for C and C++ programs \cite{esbmc2018}.

ESBMC's architecture can be summarized in three stages: (I) a front-end that can read and compile C/C++ codes, where the formal specification of the system to be verified is first treated; (II) preprocessing steps to deal with the representation of the code, control flow and unwinding of loops, and the simplification of the algorithm, aiming to reduce the computational complexity; and finally (III) the solver, where all the constraints and properties of the system to be verified are coded in SMT format and solved.

@@

If the SMT formula is shown to be satisfiable, a counterexample is presented; if the formula is find to be unsatisfiable, there are no errors up to the unwinding bound, and this result is presented. 

@@

%\subsection{Cyber-physical systems x Energy x ESBMC}
%According \cite{UC}, cyber-physical systems (CPS) are integrations of computation, networking, and physical processes. Embedded computers and networks monitor and control the physical processes, with feedback loops where physical processes affect computations and vice-versa. The economic and societal potential of such systems is vastly greater than what has been realized, and major investments are being made worldwide to develop the technology. The technology builds on the discipline of embedded systems (computers and software embedded in devices) whose principle mission is not computation, such as cars, toys, medical devices, and scientific instruments. CPS integrates the dynamics of the physical processes with those of the software and networking, providing abstractions and modeling, design, and analysis techniques for the integrated whole. 
%
%Energy production, distribution, and optimization are all CPS problems, mas mentioned in \cite{UC}. For example, the smart grid combines multiple electric power production plants with a multiplicity of loads using dynamic load balancing and dynamic pricing with demand-response strategies. Smart buildings integrate sensors into control systems for lighting, HVAC (heating, ventilation, and air conditioning), and safety (as fire monitoring and evacuation). 
%
%Therefore, in the context of this proposal, a cyber-physical system, specifically a solar photovoltaic system, will be mathematically modeled. Then a model checking will be performed to do a verification of the project in order to guarantee that the design of a stand-alone PV solution will meet the requirements, specifications and regulations. 
%
%As described in \cite{Alur}, in program verification, it is aimed to check if a program satisfies its logical specification. Contemporary verification tools vary widely in terms of source languages, verification methodology, and the degree of automation, but they all rely on repeatedly invoking an SMT solver. This work tracks the same path. 
%
%----------------------------------------
\section{Methodology }
\label{sec:Methodology}
%----------------------------------------
%
%Fig. \ref{fig:statetransition} shows the state diagram for the proposed tool. 
%
%\begin{figure}[h]
%\includegraphics[width=0.5\textwidth]{statetransition}
%\centering
%\caption{State transition diagram to the proposed automated verification.}
%\label{fig:statetransition}
%\end{figure}
%
%It is worth mentioning that the steps described here are carried out shortly after the design of the solar photovoltaic system, as soon as the equipment and equipment specifications are defined; before buying and deploying them, as a way to ensure that the project will not fail. 
%
The flowchart of the proposed automated verification tool is illustrated in Fig.~\ref{fig:flowchartgeneral}. 
As Step 01, the PV input data (load power demand, load consumption of energy, the PV system project sizing data, and the manufacturer's data-sheet information), the formulas to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as an ANSI-C code \cite{ANSI2018}. At Step 02, occurs the sizing check of the PV system to make sure that the components followed accepted international requirements toward a well designed PV project.

\begin{figure}[h]
\includegraphics[width=0.4\textwidth]{flowchart_verification3.png}
\centering
\caption{Flowchart of the proposed automated verification of PV systems.}
\label{fig:flowchartgeneral}
\end{figure}

The weather data (solar irradiance, and ambient temperature by default) will be evaluated by the ESBMC verification engine, in Step 03, based on maximum and minimum values from the site, where the PV system will be deployed. In addition, depending on one of the requirements of the system, as autonomy of the batteries, or the offer of the energy, or even the power supply from the system to check whether it is not accomplished or satisfied, the tool accuses a failure, and the diagnostic counterexample shows in which condition the fail/violation happened. 
%; as the  state of charge of the batteries, load demand of power and the load consumption of energy if defined by the code
% (as reliability, performance, or safety)

In a nutshell, ESBMC will process the C code with constraints %($C$) 
and properties %($P$) 
from the PV system that were inputted by the user, and the tool will verify automatically if the requirements are met. If the return is a fail, then the tool details the condition of violation, i.e., the state of each variable related to the system. That information can be used as a feedback to improve the PV system project. However, if the verification succeeds, the PV system will present its intended behavior at the field.
%
%
%---------------------------------------------------------------------
% \subsection{The case studies and the Algorithm}
%---------------------------------------------------------------------
%
% 
%and as backup at night 
%
%The 700 W system: 3 x 325 W PV panels connected in series, controller of 150 V/35 A with a DC-bus of 24 V, 4 x 220 Ah batteries (2 in series and 2 in parallel arrangement), and inverter of 700 W. 
%
%And the 1,200 W PV system: 4 x 325 W connected in series PV panels, with controller of 150 V/35 A  in a DC-bus of 48 V, 4 batteries of 120 Ah connected in series, and a 1,200 W inverter.
%
%As demonstrated at this work, the performance of the system is highly dependent of solar irradiance and temperature, that are specific of the deployed local (latitude and longitude).

Algorithm~\ref{alg:verification-algorithm} describes the pseudo code used to perform the automated verification. The line 1 indicates function call that performs the size checking of the entire PV system: using \eqref{eq:NTPmin}, \eqref{eq:NTP}, \eqref{eq:NPSmin}, \eqref{eq:NPS}, \eqref{eq:NPP}, and \eqref{eq:NPPmin} to verify the PV panel; using \eqref{eq:Cbank}, \eqref{eq:Nbtotal}, and \eqref{eq:batcheck} to verify the batteries; using \eqref{eq:vcvsystem}, \eqref{eq:icmin}, and \eqref{eq:icicmin} to verify the charge controller; and using \eqref{eq:vindc}, \eqref{eq:voutac}, and \eqref{eq:invcheck} to verify the inverter. The verification is done by standard \textit{assert} macro from C language to each equation. The argument to \textit{assert} must be true when the macro is executed, otherwise the program aborts and prints an error message. If there is no fail, the algorithm goes on and the batteries are assumed to have SOC of 80\% (line 5).

%At both case studies, it was considered 21 years of historic data from Manaus. 
%According with X and Y, t
Information related to average temperature ($T$) and solar irradiance ($G$), maximum and minimum annual, are passed to algorithm at lines 7 to 10 using the feature of non-deterministic variable from ESBMC to explore all the possible states from the variables and the \textit{assume} macro to limit the values considering a range. 
%and irradiance varies from 0 W/m$^{2}$ to 852 W/m$^{2}$ (with minimum of 274 W/m$^{2}$ during the daytime, when there is sunlight). 
%there is PV generation only between 8:00 h and 16:00 h every day, 
%with zero electric energy generation from 18:00 h to 6:00 h of the next day; and with insignificant generation from 6:00 h to 8:00 h, and from 16:00 h to 18:00 h of the same day. 
In order to reduce the computational effort of the algorithm,
% caused by the state explosion inherent of the technique, 
every 24h-day was considered as a time-step of 1 hour, and it was divided in 2 parts: (a) one that there is PV generation, during daylight, with a duration in hours depending on each site; and (b) one the includes all the rest of the day (without PV generation). Therefore the proposed methodology depends on the  specific data about the solar irradiation levels in order to define the average amount of hours of PV generation.

Following, the model from PV generator is used at the function call of line 11, to produce the voltage and current considering the actual $G$ and $T$. Following, related to every hour considered, the conditional \textit{if-else-endif} statements from lines 12, 17, 23 and 28, will perform the charge and discharge of batteries according the PV generation, the updated state of charge of batteries, the house's load and the set-up information of the system.
After this process is started the battery autonomy verification, from line 31. Based on the fact that won't be PV generation after a given time of the day, the algorithm will only discharge the batteries until a new charging process (at the next day) to start. The formal verification is guaranteed by \textit{assert} macro to specific variables of the model, according lines 27 and 35.
% and the non-deterministic variables $G$ and $T$ are considered during the formal verification of the system, otherwise, during the other two periods, there is no PV generation and just the power consumption from the backup batteries. 
%Within this 8h-period, $G$ and $T$ are automated verified with different values every one hour.
%, and change their value every 1 h according with the algorithm created using the technique.

@@

Experimental setup of automated verification tool: all experiments were conducted on an otherwise idle Intel Core i7-2600 (8-cores), with 3.4 GHz and 64 GB of RAM, running Ubuntu 18.04.1 LTS 64-bits. Concerning the SMT tool, ESBMC v5.1 was used with the incremental parameter in order to reduce the memory usage. At this paper, it was used the Z3 solver \cite{DeMoura} with version 4.7.1.

>>>>

However, there is a main disadvantage of model checking: the state explosion problem. In order to solve this problem, many different techniques were developed at the last decades. One of the first major advances was symbolic model checking with binary decision diagrams (BDDs). In this approach, a set of states is represented by a BDD instead of by listing each state individually, which is often exponentially smaller in practice. Another major advance is the partial order reduction, which exploits the independence of actions in a system with asynchronous composition of processes. A third major advance is counterexample-guided abstraction refinement, which adaptively tries to find an appropriate level refinement, not burdened with irrelevant detail that slows down verification \cite{Clarke2012}. However, one of the most promising approaches is Bounded Model Checking (BMC)~\cite{DBLP:conf/tacas/BiereCCZ99}.

BMC is a method that checks the model up to a given path in the path length. BMC algorithms traverse a finite state machine for a fixed number of steps, $ k $, and checks whether violation occurs with this bound. It uses Boolean Satisfiability (SAT) or Satisfiability Module Theories (SMT) solvers. SAT problem is a problem of determining whether there are certain conditions or interpretations that satisfy a given Boolean expression \cite{ClarkeHV18}. 
SMT decides the satisfiability of first-order formulae using a combination of different background theories and thus generalizes propositional satisfiability by supporting uninterpreted functions, linear and non-linear arithmetic, bit-vectors, tuples, arrays, and other decidable first-order theories~\cite{ClarkeHV18}.
The SAT or SMT solvers would search the model for conditions (value of variables) that would make the formula satisfiable. If a SAT or SMT solver finds a substitution for the formula/function then the substitute induces a counterexample.  
%
%CBMC is considering the best-known model verification tool to validate code in ANSI-C and C++ \cite{Kroening}. 
%
%\textcolor{red}{ESBMC does not use CBMC as its main frontend. Please take a look at this paper and cite it: https://ssvlab.github.io/lucasccordeiro/papers/ase2018.pdf. I would also suggest to remove the above sentence.}
%
ESBMC is one of the most representatives bounded model checkers for embedded C/C++ software based on SMT solvers~\cite{esbmc2018}. %, which can use CBMC as front-end.
%The use of SMT, instead of Boolean Satisfiability SAT from the original BMC, 
ESBMC comes as an alternative to overcome limitations of the systems modeling, especially considering that the complexity of these is increasing and the SMT method has high level and richer theories than the SAT to represent the models.

%--------------------------------------
\subsection{ESBMC}
%--------------------------------------

ESBMC (or Efficient SMT-based Bounded Model Checker) is an open source, permissively licensed (Apache 2), cross platform bounded model checking for C and C++ programs \cite{esbmc2018}. 
ESBMC's architecture can be summarized in three stages: (I) a front-end that can read and compile C/C++ codes, where the formal specification of the system to be verified is first treated; (II) preprocessing steps to deal with the representation of the code, control flow and unwinding of loops, and the simplification of the algorithm, aiming to reduce the computational complexity; and finally (III) the solver, where all the constraints and properties of the system to be verified are encoded into SMT format and solved.

@@

If the SMT formula is shown to be satisfiable, a counterexample is presented; if the formula is find to be unsatisfiable, there are no errors up to the unwinding bound. 

@@

%\subsection{Cyber-physical systems x Energy x ESBMC}
%According \cite{UC}, cyber-physical systems (CPS) are integrations of computation, networking, and physical processes. Embedded computers and networks monitor and control the physical processes, with feedback loops where physical processes affect computations and vice-versa. The economic and societal potential of such systems is vastly greater than what has been realized, and major investments are being made worldwide to develop the technology. The technology builds on the discipline of embedded systems (computers and software embedded in devices) whose principle mission is not computation, such as cars, toys, medical devices, and scientific instruments. CPS integrates the dynamics of the physical processes with those of the software and networking, providing abstractions and modeling, design, and analysis techniques for the integrated whole. 
%
%Energy production, distribution, and optimization are all CPS problems, mas mentioned in \cite{UC}. For example, the smart grid combines multiple electric power production plants with a multiplicity of loads using dynamic load balancing and dynamic pricing with demand-response strategies. Smart buildings integrate sensors into control systems for lighting, HVAC (heating, ventilation, and air conditioning), and safety (as fire monitoring and evacuation). 
%
%Therefore, in the context of this proposal, a cyber-physical system, specifically a solar photovoltaic system, will be mathematically modeled. Then a model checking will be performed to do a verification of the project in order to guarantee that the design of a stand-alone PV solution will meet the requirements, specifications and regulations. 
%
%As described in \cite{Alur}, in program verification, it is aimed to check if a program satisfies its logical specification. Contemporary verification tools vary widely in terms of source languages, verification methodology, and the degree of automation, but they all rely on repeatedly invoking an SMT solver. This work tracks the same path. 
%
%----------------------------------------
\section{Methodology }
\label{sec:Methodology}
%----------------------------------------
%
%Fig. \ref{fig:statetransition} shows the state diagram for the proposed tool. 
%
%\begin{figure}[h]
%\includegraphics[width=0.5\textwidth]{statetransition}
%\centering
%\caption{State transition diagram to the proposed automated verification.}
%\label{fig:statetransition}
%\end{figure}
%
%It is worth mentioning that the steps described here are carried out shortly after the design of the solar photovoltaic system, as soon as the equipment and equipment specifications are defined; before buying and deploying them, as a way to ensure that the project will not fail. 
%
The flowchart of the proposed automated verification tool is illustrated in Fig.~\ref{fig:flowchartgeneral}. 
As Step 1, the PV input data (e.g., load power demand and load consumption of energy), the formulas to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as an ANSI-C code~\cite{ANSI2018}. In Step 2, occurs the sizing check of the PV system to make sure that the components accepted international requirements toward a well designed PV project.

\begin{figure}[h]
\includegraphics[width=0.4\textwidth]{flowchart_verification3.png}
\centering
\caption{Flowchart of the proposed automated verification of PV systems. \textcolor{red}{replace 01, 02 and 03 by 1, 2, 3.}}
\label{fig:flowchartgeneral}
\end{figure}

The weather data (e.g., solar irradiance and ambient temperature by default) will be evaluated by the ESBMC verification engine, in Step 3, based on maximum and minimum values from the site, where the PV system will be deployed. In addition, depending on one of the requirements of the system, as autonomy of the batteries, or the offer of the energy, or even the power supply from the system to check whether it is not accomplished or satisfied, ESBMC accuses a failure, and the diagnostic counterexample shows in which condition the fail/violation happened. 
%; as the  state of charge of the batteries, load demand of power and the load consumption of energy if defined by the code
% (as reliability, performance, or safety)

\textcolor{red}{In the following paragraph you should related the output of our verification engine with the description of the BMC SAT or UNSAR given above. For example, what does a failure mean? is it SAT?}
In a nutshell, ESBMC will process the C code with constraints %($C$) 
and properties %($P$) 
from the PV system that were provided by the user, and the tool will verify automatically if the requirements are met. If the return is a failure, then the tool details the condition of violation, i.e., the state of each variable related to the system. That information can be used as a feedback to improve the PV system project. However, if the verification succeeds, the PV system will present its intended behavior at the field.
%
%
%---------------------------------------------------------------------
% \subsection{The case studies and the Algorithm}
%---------------------------------------------------------------------
%
% 
%and as backup at night 
%
%The 700 W system: 3 x 325 W PV panels connected in series, controller of 150 V/35 A with a DC-bus of 24 V, 4 x 220 Ah batteries (2 in series and 2 in parallel arrangement), and inverter of 700 W. 
%
%And the 1,200 W PV system: 4 x 325 W connected in series PV panels, with controller of 150 V/35 A  in a DC-bus of 48 V, 4 batteries of 120 Ah connected in series, and a 1,200 W inverter.
%
%As demonstrated at this work, the performance of the system is highly dependent of solar irradiance and temperature, that are specific of the deployed local (latitude and longitude).

Algorithm~\ref{alg:verification-algorithm} describes the pseudocode used to perform the automated verification. Line 1 indicates a function call that performs the size checking of the entire PV system: using \eqref{eq:NTPmin}, \eqref{eq:NTP}, \eqref{eq:NPSmin}, \eqref{eq:NPS}, \eqref{eq:NPP}, and \eqref{eq:NPPmin} to verify the PV panel; using \eqref{eq:Cbank}, \eqref{eq:Nbtotal}, and \eqref{eq:batcheck} to verify the batteries; using \eqref{eq:vcvsystem}, \eqref{eq:icmin}, and \eqref{eq:icicmin} to verify the charge controller; and using \eqref{eq:vindc}, \eqref{eq:voutac}, and \eqref{eq:invcheck} to verify the inverter. The verification is performed by the standard \textit{assert} macro from ANSI-C programming language to each equation. The argument to \textit{assert} must be \textit{true} when the macro is executed; otherwise, the program aborts and prints an error message. If there is no fail, the algorithm goes on and the batteries are assumed to have SOC of 80\% (line 5).

%At both case studies, it was considered 21 years of historic data from Manaus. 
%According with X and Y, t
Information related to average temperature ($T$) and solar irradiance ($G$), maximum and minimum annual, are given to the algorithm in Lines 7 to 10 using the feature of non-deterministic variables from ESBMC to explore all possible states and the \textit{assume} macro to limit the non-deterministic values considering a given range. 
%and irradiance varies from 0 W/m$^{2}$ to 852 W/m$^{2}$ (with minimum of 274 W/m$^{2}$ during the daytime, when there is sunlight). 
%there is PV generation only between 8:00 h and 16:00 h every day, 
%with zero electric energy generation from 18:00 h to 6:00 h of the next day; and with insignificant generation from 6:00 h to 8:00 h, and from 16:00 h to 18:00 h of the same day. 
In order to reduce the computational effort of the algorithm,
% caused by the state explosion inherent of the technique, 
every 24h-day was considered as a time-step of 1 hour, and it was split into two parts: (a) one that there is PV generation, during daylight, with a duration in hours depending on each site; and (b) one that includes all the remaining day (without PV generation). Therefore, the proposed methodology depends on specific data about the solar irradiation levels to define the average amount of hours of PV generation.

After that, the model from PV generator is used in the function call of Line 11, to produce the voltage and current considering the actual $G$ and $T$. Following, related to every hour considered, the conditional \textit{if-else-endif} statements from lines 12, 17, 23 and 28, will perform the charge and discharge of batteries according to the PV generation, the updated state of charge of batteries, the house's load and the set-up information of the system.
\textcolor{red}{this sentence is unclear... After this process is started the battery autonomy verification, from line 31}. \textcolor{red}{this sentence is unclear... Based on the fact that won't be PV generation after a given time of the day, the algorithm will only discharge the batteries until a new charging process (at the next day) to start.} \textcolor{red}{what do you mean by The formal verification is guaranteed?...  The formal verification is guaranteed by \textit{assert} macro to specific variables of the model, according lines 27 and 35.}
% and the non-deterministic variables $G$ and $T$ are considered during the formal verification of the system, otherwise, during the other two periods, there is no PV generation and just the power consumption from the backup batteries. 
%Within this 8h-period, $G$ and $T$ are automated verified with different values every one hour.
%, and change their value every 1 h according with the algorithm created using the technique.

@@

Experimental setup of automated verification tool: all experiments were conducted on an otherwise idle Intel Core i7-2600 (8-cores), with 3.4 GHz and 64 GB of RAM, running Ubuntu 18.04.1 LTS 64-bits. Concerning the SMT tool, ESBMC v5.1 was used with the incremental parameter to reduce the memory usage. At this paper, it was used the Z3 solver \cite{DeMoura} with version 4.7.1.
